### 2023-03-01 editorial-communication/response-to-the-reviewers.Qmd

> In addition to increasing scientific rigour and confidence in ecological software (Scheller et al., 2010), automation can help advance more rapidly sharing ecological data and making sure the data are high quality (Dietze et al., 2018). Integrating automation workflows has been highly encouraged in areas of EEB, including predictive ecology (McIntire et al., 2022), long-term ecological studies (Ernest et al., 2018; Yenni et al., 2019), and management of species at risk information (Naujokaitis-Lewis et al., 2022).

:::

##### **R2.5.** Related to Major Comments 1 and 4, given that the focus of the paper is toward integration into EEB scientific research workflows, I suggest adding another figure (or replacing Figure 1) that details a generalized scientific research workflow (e.g., Munafò et al. 2017 <https://www.nature.com/articles/s41562-016-0021>) and how Github supports/augments that workflow. This could relate to or build on Table 2, which a useful summarization of important features as they relate to different research participants. {#sec-R2.5}

::: {#ResponseR25 .response}
We thank you for this comment. We discussed amd attempted to associate the use cases to hypothetical versions of the scientific method and academic roles. Despite enjoying the idea of a figure resembling Figure 1 from Munafò et al. 2017 (Nature), we have not been able to produce a figure that would not feel polluted or redundant with Figure 2. We have attempted this with a circular flow, stacked bar chart, or a network graph. The issue is that most use cases are related to many stages of the scientific process. The exception are "Academic websites" and "Educational materials", which may contribute to research development, but more marginally in relation to the other use cases. We appreciate the suggestion and would be happy to come to back it if you think it is important for our study.
:::

### 2023-03-01 manuscript.tex
Update response-to-the-reviewers.Qmd [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f105568d200daed275bf3735ef04dd1b237642b8.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/f105568d200daed275bf3735ef04dd1b237642b8/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4307394423

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/bab6e3fbfbc8e0e7e619032dc0976b53d321f9e8/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/bab6e3fbfbc8e0e7e619032dc0976b53d321f9e8}{SORTEE-Github-Hackathon/manuscript@bab6e3f}
on March 1, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/f105568d200daed275bf3735ef04dd1b237642b8/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/f105568d200daed275bf3735ef04dd1b237642b8}{SORTEE-Github-Hackathon/manuscript@f105568}
on March 1, 2023.
